---
title: "SDS 192: Problem Set 7"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

#### GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Here is some Code

You can include R code in the document as follows:

```{r cars}
glimpse(cars)

summary(cars)
```

------------

## Visualizations Go Here

You can also embed plots.   
      
**For example:**

```{r pressure, echo = FALSE}
ggplot(data = pressure, aes(x = temperature, y = pressure)) + geom_point() + geom_smooth(se = FALSE) + labs(title = "This is the same plot using ggplot")
```

```{r, echo = FALSE, message = FALSE}
ggplot(cars, aes(x = speed, y = dist)) + geom_point() + labs(x = "Speed (mph)", y = "Stopping Distance (ft)", title = "Speed vs. Stopping Distance for 1920s Cars") + geom_smooth(method = "lm", se = FALSE)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
